---
title: "The impact of renewable energy production on supply-demand balance and carbon emissions in Turkey"
---

Welcome to my project page.

Keep an eye on this space to stay updated with my project activities.

# 1. Project Overview and Scope

The share of renewable energy production in the total energy supplied and demanded in Turkey changes every year. In this project, first the supply-demand relationship and the effect of renewable energy on this will be examined, and then the effect of renewable energy on carbon emissions will be examined.

# 2. Data

Data required for investigations in the project:

<a href="https://seffaflik.epias.com.tr/electricity/electricity-generation/ex-post-generation/real-time-generation">Real-time production data in Turkey between 2015-2020</a>

```{r}
#install.packages("readxl")
library(readxl)
prod_2015 <- read_excel("C:\\Users\\irems\\Documents\\GitHub\\emu660-spring2024-iremshasturk\\assets\\Real-Time_Generation-2015.xlsx")
head(prod_2015)

```

{r}

## 2.1 Data Source

Data is obtained from EPİAŞ Transparency Platform.

<a href="https://seffaflik.epias.com.tr/electricity/electricity-generation/ex-post-generation/real-time-generation">Real-time production data in Turkey between 2015-2020</a>

## 2.2 General Information About Data

xxxxxx

## 2.3 Reason of Choice

xxxxxx

## 2.4 Preprocessing

Due to data complexity, hourly data converted to monthly data. Thus, it has become easier to examine. Data obtained for 2015 after preprocessing:

```{r}

prod_monthly_2015 <- read_excel("C:\\Users\\irems\\Documents\\GitHub\\emu660-spring2024-iremshasturk\\assets\\Real-Time_Generation-monthly_2015.xlsx")
prod_monthly_2020 <- read_excel("C:\\Users\\irems\\Documents\\GitHub\\emu660-spring2024-iremshasturk\\assets\\Real-Time_Generation-monthly_2020.xlsx")
head(prod_monthly_2015)
head(prod_monthly_2020)

chooseCRANmirror(ind=1)
install.packages("ggplot2") 
library(ggplot2)


combined_data <- rbind(prod_monthly_2015, prod_monthly_2020)
combined_data$Year <- factor(rep(c("2015", "2020"), each = nrow(prod_monthly_2015)))


ggplot(combined_data) +
  geom_line(aes(x = Date, y = Total, color = Year, group=Year))

ggplot(combined_data) +
  geom_line(aes(x = Date, y = Solar, color = Year, group=Year))
```

{r} #install.packages("readxl") library(readxl) prod_2015 \<- read_excel("C:\\Users\\irems\\Documents\\GitHub\\emu660-spring2024-iremshasturk\\assets\\Real-Time_Generation-2015.xlsx") head(prod_2015)

# 3. Analysis

xxxxxx

## 3.1 Exploratory Data Analysis

```{r}
#total_dogalgaz <- sum(uretim_2015$Doğal gaz)
```

## 3.2 Trndefinedend Analysis

xxxxxx

## 3.3 Model Fitting

xxxxxx

## 3.4 Results

xxxxxx

# 4. Results and Key Takeaways

xxxxxx
